The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
integrate kivela syntax, mv some to comment

#### Network types and construction (defining layers for the multilayer network)
<!-- specific kivela name, 6 layer multilayer-->

Following [@Kivela_2014]:

* we generated a six layer multilayer social network consisting of two aspects
(season and landcover)
* elementary-layer sets for two seasons (winter and summer) and three landcover
classes (open, forest and lichen).
* This multilayer network is not node-aligned as not all individuals exist on
all layers
* This layer has both ordinal and categorical coupling

@@

We generated seasonal multilayer social networks consisting of habitat-specific
monolayers. Each layer was the social association network generated in one of
three habitat types (lichen, open, and forest). For habitat-specific networks,
all GPS relocations were assigned to the corresponding habitat type and
proximity-based social network layers were generated using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].

>>>>

#### Network types and construction (defining layers for the multilayer network)

<!-- should use something like "using syntax from Kivela 2014..." or 
Following [@Kivela_2014]:
other info to maybe include: the multilayer network was not node-aligned since
not all individuals were on all layers
the temporal aspect is ordinal coupling and landcover aspect is categorical coupling

@@

-->

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were the social association network generated in
each season and landcover combination. Proximity-based social network layers
were generated using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].
